Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-07-29 paper/ms.tex
update manuscript with pretty plots
update manuscript

Finding and studying systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$Gyr, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting
V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
not detect the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.

@@

With the aim of advancing the young planet census, we have been using
data from the TESS spacecraft \citep{ricker_transiting_2015} to
perform a Cluster Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time of writing, we had made $\sim$$6\times10^5$ light curves from
the first year of TESS observations. The light curves are available at
MAST\footnote{\stscilink}, and through \datasetlink.  Searching
through a subset of these light curves brought our attention to the
candidate transiting planet, \pn, that is the subject of this
analysis.

The transits of \pn\ are grazing the stellar limb, which is a cause
for concern.  Particularly for a target near the galactic plane
($b=-5.8^\circ$), background eclipsing binaries are a major source of
astrophysical false positives \citep[{\it
e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data show that this
and related scenarios are unlikely to the degree that we can
``validate'' the planet, {\it i.e.}, determine that its probability of
being an astrophysical false positive is negligibly small.  We
considered this result worth reporting because of the planet's youth.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.65\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  Neighbors are as
  in Figure~\ref{fig:hr}. $\alpha$ denotes right ascension, $\delta$
  declination, $\pi$ parallax, $\mu_{\rm \delta}$ and $\mu_{\rm
  \alpha}$ proper motion in each equatorial direction, and ${\rm RV}$
  radial velocity reported by Gaia DR2.  The RVs are for unblended
  spectra of bright stars ($G\lesssim 12$).  The proper motion
  projection ($\mu_{\delta}$ vs{.} $\mu_{\rm \alpha}\cos\delta$)
  highlights incompleteness in the membership selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} Contours are shown at 1, 2, 3,
    and 4-$\sigma$ confidence.  The planet-to-star size ratio
    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
    This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Planet radii versus ages, for the known transiting planets.} 
    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
    are from the NASA Exoplanet Archive on 13 July 2020.  Precise ages
    are known for only a small fraction of the gray points.
		\label{fig:rpvsage}
	}
	\vspace{-0.5cm}
\end{figure}

@@

The Rossiter-McLaughlin approach is more likely to yield short-term
success than a direct mass measurement because of the RV noise
expected to be induced by stellar rotation.  The photometric amplitude
induced by starspots on \tn\ is $\approx 2\%$.  The spot-induced RV
variation expected over the course of the $\approx 3\,{\rm d}$
rotation period can be estimated by multiplying the photometric
amplitude and spectroscopic equatorial velocity.  This gives
$\sigma_{\rm RV,rot} \approx 300\,{\rm m\,s}^{-1}$, and is consistent
with the scatter we observe in our radial velocities from FEROS.
Detecting the radial velocity signature of a planet's Keplerian motion
in this regime is challenging, and requires a significant amount of
data and care in signal extraction \citep{barragan_radial_2019}.  The
Rossiter-McLaughlin measurement avoids the majority of this issue
because the transit occurs over a much shorter duration than a single
stellar rotation period.

@@

%\clearpage
\acknowledgements
\raggedbottom

>>>>

Finding and understanding systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$Gyr, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting
V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
not confirm the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.

@@

To advance the young planet census, we have been using data from the
TESS spacecraft \citep{ricker_transiting_2015} to perform a Cluster
Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time of writing, we had made $\sim$$6\times10^5$ light curves from
the first year of TESS observations. The light curves are available at
MAST\footnote{\stscilink}, and through \datasetlink.  Searching
through a subset of these light curves brought our attention to the
candidate transiting planet, \pn, that is the subject of this
analysis.

The transits of \pn\ are grazing the stellar limb, which is a cause
for concern.  Particularly for a star near the galactic plane
($b=-5.8^\circ$), background eclipsing binaries are a major source of
astrophysical false positives \citep[{\it
e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data show that this
and related scenarios are unlikely to the degree that we can
validate the planet, {\it i.e.}, determine that its probability of
being an astrophysical false positive is negligibly small.  We
considered this result worth reporting because of the planet's youth.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.65\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  Neighbors are as
  in Figure~\ref{fig:hr}. $\alpha$ denotes right ascension, $\delta$
  declination, $\pi$ parallax, $\mu_{\rm \delta}$ and $\mu_{\rm
  \alpha}$ proper motion in each equatorial direction, and ${\rm RV}$
  radial velocity reported by Gaia DR2.  The RVs are for unblended
  spectra of bright stars ($G\lesssim 12$).  The proper motion
  projection ($\mu_{\delta}$ vs{.} $\mu_{\rm \alpha}\cos\delta$)
  highlights incompleteness in the membership selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} Contours are shown at 1, 2, 3,
    and 4-$\sigma$ confidence.  The planet-to-star size ratio
    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
    This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Planet radii versus ages, for the known transiting planets.} 
    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
    are from the NASA Exoplanet Archive on 29 July 2020.  Precise ages
    are known for only a small fraction of the gray points.
		\label{fig:rpvsage}
	}
	\vspace{-0.2cm}
\end{figure}

@@

The Rossiter-McLaughlin approach is more likely to yield short-term
success than a direct mass measurement because of the RV noise
expected to be induced by stellar rotation.  The photometric amplitude
induced by starspots on \tn\ is $\approx 2\%$.  The spot-induced RV
variation expected over the course of the $\approx 3\,{\rm d}$
rotation period can be estimated by multiplying the photometric
amplitude and spectroscopic equatorial velocity.  This gives
$\sigma_{\rm RV,rot} \approx 300\,{\rm m\,s}^{-1}$, and is consistent
with the scatter we observe in our radial velocities from FEROS.
Detecting a planet's Keplerian motion in this regime is challenging,
and requires a significant amount of data and care in signal
extraction \citep{barragan_radial_2019}.  The Rossiter-McLaughlin
measurement avoids the majority of this issue because the transit
occurs over a much shorter duration than a single stellar rotation
period.

@@

\clearpage
\acknowledgements
\raggedbottom
